---
title: "random_graphs"
author: "Ashish"
date: "11/9/2021"
output: html_document
---

```{r}
library(tidyverse)
```

# Generate random graph from process of task

```{r}
n_sims <- 1000
n_stimuli <- 25
n_trials <- 100
produce_random_graph <- function(n_trials=n_trials, n_stimuli=n_stimuli){
  stimuli <- paste0("stim_", 1:n_stimuli)
  stimuli_grid <- expand_grid(v1=stimuli, v2=stimuli, v3=stimuli) %>% 
    filter(v1 > v2 & v2 > v3) %>% 
    sample_frac()
  trial_result <- tibble(node1=rep(NA, n_trials*3), 
                         node2=rep(NA, n_trials*3), 
                         chosen=rep(NA, n_trials*3))
  for(trial_num in (1:n_trials)-1){
    stim <- unlist(stimuli_grid[trial_num+1, ])
    chosen <- stim %>% 
      sample(2) %>% 
      sort
    unchosen <- stim[!stim %in% chosen]
    trial_result[(3*trial_num)+1,"node1"] <- chosen[1]
    trial_result[(3*trial_num)+1,"node2"] <- chosen[2]
    trial_result[(3*trial_num)+1,"chosen"] <- 1
    trial_result[(3*trial_num)+2,"node1"] <- sort(c(chosen[1], unchosen))[1]
    trial_result[(3*trial_num)+2,"node2"] <-  sort(c(chosen[1], unchosen))[2]
    trial_result[(3*trial_num)+2,"chosen"] <- 0
    trial_result[(3*trial_num)+3,"node1"] <-  sort(c(chosen[2], unchosen))[1]
    trial_result[(3*trial_num)+3,"node2"] <-  sort(c(chosen[2], unchosen))[2]
    trial_result[(3*trial_num)+3,"chosen"] <- 0
  }
  
  df_edges <- trial_result %>% 
    group_by(node1, node2) %>% 
    summarize(weight = mean(chosen), .groups="drop") %>% 
    filter(weight > 0)
  g <- df_edges %>% 
    graph_from_data_frame(directed=FALSE)
  E(g)$weight <- df_edges$weight
  return(g)
}
df_rand_graphs <- tibble(graph = map(1:n_sims, ~produce_random_graph(n_trials, n_stimuli)))
df_rand_graphs_stats <- df_rand_graphs %>% 
  # mutate(cluster = map(graph, cluster_walktrap)) %>%
  mutate(cluster = map(graph, cluster_louvain)) %>%
  mutate(modularity = map_dbl(cluster, modularity)) %>% 
  mutate(transitivity = map_dbl(graph, transitivity)) %>% 
  mutate(transitivity_weighted = map_dbl(graph, ~mean(transitivity(., "weighted", isolates="zero")))) %>% 
  mutate(n_clusters = map_dbl(cluster, ~length(unique(.$membership)))) %>% 
  
  mutate(adjacency_mat = map(graph, ~get.adjacency(., attr="weight", sparse=FALSE))) %>% 
  mutate(sparsity = map_dbl(adjacency_mat, ~ mean(. == 0))) %>% 

    mutate(adjacency_mat_sparse = map(graph, ~get.adjacency(., attr="weight", sparse=TRUE))) %>% 
  mutate(tsvd = map(adjacency_mat_sparse, ~sparsesvd::sparsesvd(.) )) %>% 
  mutate(tsvd_pr_var = map(tsvd, ~.$d/sum(.$d) )) %>% 
  mutate(density = map_dbl(graph, edge_density)) %>% 
  ungroup

df_rand_graphs_stats %>% 
  ggplot(aes(x = transitivity_weighted)) + 
  geom_histogram(bins=30) + 
  geom_vline(xintercept = df_rand_graphs_stats$transitivity_weighted %>% mean)
  
df_rand_graphs_stats$transitivity_weighted %>% mean
df_rand_graphs_stats$transitivity_weighted %>% sd
df_rand_graphs_stats$transitivity_weighted %>% sd/sqrt(n_sims)


df_rand_graphs_stats %>% 
  ggplot(aes(x = density)) + 
  geom_histogram(bins=50)

df_rand_graphs_stats$modularity %>% mean
df_rand_graphs_stats %>% 
  ggplot(aes(x = modularity)) + 
  geom_histogram(bins=50)



cor.test(df_rand_graphs_stats$density, df_rand_graphs_stats$transitivity_weighted)
cor.test(df_rand_graphs_stats$modularity, df_rand_graphs_stats$transitivity_weighted)
cor.test(df_rand_graphs_stats$modularity, df_rand_graphs_stats$density)
```

## Generate random graph from transitivity focused experiment design

### by adj matrix
Here I design an algorithm to specifically participants' transitivity. 

1. Present random trials with constraint of showing all images at least once. With 25 images, we can do this in 9 trials. 

2. For each trial, look in adjacency matrix in each column for incomplete triangles. Select incomplete triangles that have  
```{r}

n_stimuli <- 9
n_trials <- 48
stimuli <- paste0("stim_", str_pad((1:n_stimuli), 2, pad="0"))

# initial_stimuli_grid <- expand_grid(v1=stimuli, v2=stimuli, v3=stimuli) %>%
#   filter(as.numeric(substr(v1, 6, 7)) - as.numeric(substr(v2, 6, 7)) == -1 &
#            as.numeric(substr(v2, 6, 7)) - as.numeric(substr(v3, 6, 7)) == -1)
initial_stimuli_grid <- matrix(stimuli, byrow = T, nrow = n_stimuli/3) %>%
  as_tibble(.name_repair=~c("v1", "v2", "v3"))

trial_result <- tibble(node1=rep(NA, n_trials*3), 
                       node2=rep(NA, n_trials*3), 
                       chosen=rep(NA, n_trials*3))
# -- initial random section -- #
for(trial_num in (1:nrow(initial_stimuli_grid))-1){
  stim <- unlist(initial_stimuli_grid[trial_num+1, ])
  chosen <- stim %>% 
    sample(2) %>% 
    sort
  unchosen <- stim[!stim %in% chosen]
  trial_result[(3*trial_num)+1,"node1"] <- chosen[1]
  trial_result[(3*trial_num)+1,"node2"] <- chosen[2]
  trial_result[(3*trial_num)+1,"chosen"] <- 1
  trial_result[(3*trial_num)+2,"node1"] <- sort(c(chosen[1], unchosen))[1]
  trial_result[(3*trial_num)+2,"node2"] <-  sort(c(chosen[1], unchosen))[2]
  trial_result[(3*trial_num)+2,"chosen"] <- 0
  trial_result[(3*trial_num)+3,"node1"] <-  sort(c(chosen[2], unchosen))[1]
  trial_result[(3*trial_num)+3,"node2"] <-  sort(c(chosen[2], unchosen))[2]
  trial_result[(3*trial_num)+3,"chosen"] <- 0
}

# -- second random section -- #
# creating second arm of triangle
initial_chosen <- trial_result %>% 
  filter(chosen == 1)
for(trial_num in (1:nrow(initial_chosen))-1){
  third_stim <- sample(
    stimuli[stimuli != initial_chosen[[trial_num+1, "node1"]] &
              stimuli != initial_chosen[[trial_num+1, "node2"]]],
    
    1)
  stim <- c(initial_chosen[[trial_num+1, "node1"]], 
            initial_chosen[[trial_num+1, "node2"]], 
            third_stim)
  chosen <- stim %>% 
    sample(2) %>% 
    sort
  unchosen <- stim[!stim %in% chosen]
  nrows_filled <- nrow(initial_stimuli_grid)*3
  trial_result[(3*trial_num)+1+nrows_filled,"node1"] <- chosen[1]
  trial_result[(3*trial_num)+1+nrows_filled,"node2"] <- chosen[2]
  trial_result[(3*trial_num)+1+nrows_filled,"chosen"] <- 1
  trial_result[(3*trial_num)+2+nrows_filled,"node1"] <-
    sort(c(chosen[1], unchosen))[1]
  trial_result[(3*trial_num)+2+nrows_filled,"node2"] <- 
    sort(c(chosen[1], unchosen))[2]
  trial_result[(3*trial_num)+2+nrows_filled,"chosen"] <- 0
  trial_result[(3*trial_num)+3+nrows_filled,"node1"] <- 
    sort(c(chosen[2], unchosen))[1]
  trial_result[(3*trial_num)+3+nrows_filled,"node2"] <- 
    sort(c(chosen[2], unchosen))[2]
  trial_result[(3*trial_num)+3+nrows_filled,"chosen"] <- 0
}



# -- testing transitivity (third arm of triangle) -- #

# make adjacency matrix
adj_mat <- expand_grid(node1=stimuli, node2=stimuli) %>% 
  mutate(values=0) %>% 
  pivot_wider(
    id_cols="node1",
    names_from="node2",
    values_from="values"
  ) %>% 
  select(-node1) %>% 
  as.matrix()
rownames(adj_mat) <- stimuli
trial_result_chosen <- trial_result %>% 
  filter(chosen==1)
for(i in 1:nrow(trial_result_chosen)){
  node1 <- trial_result_chosen[[i, "node1"]]
  node2 <- trial_result_chosen[[i, "node2"]]
  adj_mat[node1, node2] <- trial_result_chosen[[i, "chosen"]]
  adj_mat[node2, node1] <- trial_result_chosen[[i, "chosen"]]
}
stim_w_incomplete_triangles <- colnames(adj_mat)[colSums(adj_mat) >= 2]
random_stim_incomplete_triangle <- sample(stim_w_incomplete_triangles, 1)
adj_mat_col <- adj_mat[,random_stim_incomplete_triangle]
candidate_stim_to_test <- names(adj_mat_col[adj_mat_col==1])
trial_result



# # -- building graph -- #
# df_edges <- trial_result %>% 
#   group_by(node1, node2) %>% 
#   summarize(weight = mean(chosen), .groups="drop") %>% 
#   filter(weight > 0)
# g <- df_edges %>% 
#   graph_from_data_frame(directed=FALSE)
# E(g)$weight <- df_edges$weight



```

### other method

```{r}
n_sims <- 1000
n_stimuli <- 24
n_trials <- 50
stimuli <- paste0("stim_", str_pad((1:n_stimuli), 2, pad="0"))

produce_random_graph <- function(n_trials=n_trials, n_stimuli=n_stimuli){
  # initial_stimuli_grid <- expand_grid(v1=stimuli, v2=stimuli, v3=stimuli) %>%
  #   filter(as.numeric(substr(v1, 6, 7)) - as.numeric(substr(v2, 6, 7)) == -1 &
  #            as.numeric(substr(v2, 6, 7)) - as.numeric(substr(v3, 6, 7)) == -1)
    # sample_frac() # uncomment for simulations
  initial_stimuli_grid <- matrix(stimuli, byrow = T, nrow = n_stimuli/3) %>%
    as_tibble(.name_repair=~c("v1", "v2", "v3"))
  
  trial_result <- tibble(node1=rep(NA, n_trials*3), 
                         node2=rep(NA, n_trials*3), 
                         chosen=rep(NA, n_trials*3))
  # -- initial random section -- #
  for(trial_num in (1:nrow(initial_stimuli_grid))-1){
    stim <- unlist(initial_stimuli_grid[trial_num+1, ])
    chosen <- stim %>% 
      sample(2) %>% 
      sort
    unchosen <- stim[!stim %in% chosen]
    trial_result[(3*trial_num)+1,"node1"] <- chosen[1]
    trial_result[(3*trial_num)+1,"node2"] <- chosen[2]
    trial_result[(3*trial_num)+1,"chosen"] <- 1
    trial_result[(3*trial_num)+2,"node1"] <- sort(c(chosen[1], unchosen))[1]
    trial_result[(3*trial_num)+2,"node2"] <-  sort(c(chosen[1], unchosen))[2]
    trial_result[(3*trial_num)+2,"chosen"] <- 0
    trial_result[(3*trial_num)+3,"node1"] <-  sort(c(chosen[2], unchosen))[1]
    trial_result[(3*trial_num)+3,"node2"] <-  sort(c(chosen[2], unchosen))[2]
    trial_result[(3*trial_num)+3,"chosen"] <- 0
  }
  # -- testing transitivity -- #
  
  # pick a random node
  rand_stimulus1 <- sample(stimuli, 1)
  # look for incomplete triangles that have not been tested
  trial_result %>% 
    filter(node1==rand_stimulus1 | node2==rand_stimulus1)
  
  trial_result %>% 
    filter(node1==rand_stimulus1 | node2==rand_stimulus1)
  # if found an incomplete triangle that has not been tested
  
  # if can't find an incomplete triangle that has not been tested
  rand_stimulus2 <- sample(stimuli[stimuli!=rand_stimulus1], 1)
  rand_stimulus3 <- sample(stimuli[stimuli!=rand_stimulus1 &
                                     stimuli!=rand_stimulus2], 1)
  # test a random node
  
  
  # -- building graph -- #
  df_edges <- trial_result %>% 
    group_by(node1, node2) %>% 
    summarize(weight = mean(chosen), .groups="drop") %>% 
    filter(weight > 0)
  g <- df_edges %>% 
    graph_from_data_frame(directed=FALSE)
  E(g)$weight <- df_edges$weight
  return(g)
}
```
