---
title: "Exploratory analysis of emotion similarity networks"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---

In this document, I am conducting exploratory analyses of the recently developed emotion similarity network task. In the task, participants select which two of a set of three emotional images are most similar in their emotional quality. I hypothesize that participants who exhibit self-report characteristics of greater emotional awareness will have more distinct communities in a within person network analysis of each participants' similarity structure.




* [clustering coefficient](https://en.wikipedia.org/wiki/Clustering_coefficient)
* [small world networks](https://en.wikipedia.org/wiki/Small-world_network)
* [mean shortest path length](https://en.wikipedia.org/wiki/Distance_(graph_theory)) - determines if network is small world
    
    
# Initialization

```{r, message=FALSE}
rm(list=ls())
library(lmerTest)
library(igraph)
library(qgraph)
library(kableExtra)
library(here)
library(tidyverse)
theme_set(theme_bw())
```

```{r, eval=FALSE}
library(tidylog)
```

# Preprocessing

## Functions

```{r}
#' scale_numerics
#' 
#' z-scores values of all numeric columns
#' 
#' @param df input dataframe
#' @param new_cols boolean indicating whether to create new columns when scaling or scale in place
#' @param ... arguments to be passed to rsurveyutils::scale()
#'
#' @return dataframe with scaled values
scale_numerics <- function(df, new_cols=TRUE, ...){
  
  if(new_cols){df %>% mutate_if(is.numeric, list(sc = ~rsurveyutils::scale(., ...)))}
  else {df %>% mutate_if(is.numeric,  ~scale(., ...))}
}

```


## Read & process survey data
```{r, message=FALSE}
survey_filepath <- "data/proc/emo_similarity_network_presurvey_sum2021_proc.csv"

df_survey_raw <- read_csv(here(survey_filepath))

df_survey <- df_survey_raw %>% 
  group_by(pid) %>%
  # -- remove failed attention checks -- #
  filter((all(ac_paq_pass == 1) & 
            all(ac_pmerq_pass == 1) & 
            all(ac_tas_pass == 1))) %>% 
  # -- remove people who did it twice -- #
  filter(n() ==1) %>% 
  ungroup
```

## Read & process task data
```{r, message=FALSE}
task_filepath <- "data/proc/emoSimilarityTask_proc.csv"

df_task_raw <- read_csv(here(task_filepath))

df_task <- df_task_raw
```

## Create data frame of forced choice attention checks

Currently using a .33 minimum threshold of passing attention checks

.33 = 4 correct out of 12, 15% chance of passing threshold if you're guessing

```{r}
ac_minimum_threshold <- .83

df_ac_forceChoice <- df_task %>% 
  drop_na(ac_forceChoice) %>% 
  group_by(pid, pool) %>% 
  summarize(pr_correct = mean(ac_forceChoice)) %>% 
  ungroup
df_ac_forceChoice %>% 
  ggplot(aes(x = pr_correct)) + 
  geom_histogram()
ac_fail_pids <- df_ac_forceChoice %>% 
  filter(pr_correct < ac_minimum_threshold) %>% 
  pull(pid)

# df_ac_forceChoice %>% 
#   filter(pool == "rep" & pr_correct < .33)
  
```

## Create data frame of task trials

```{r}
df_incomplete_runs <- df_task %>% 
  group_by(pid, run_id) %>% 
  summarize(n = n()) %>% 
  filter(n < 347)

df_remove_secondTry_pids <- df_task %>% 
  filter(!run_id %in% df_incomplete_runs$run_id) %>% 
  group_by(pid, run_id) %>% 
  summarize(n = n()) %>% 
  arrange(run_id) %>% 
  slice(1)



df_trials <- df_task %>% 
  # -- keep only trials -- #
  filter(trial_type == "image-multi-select") %>%
  filter(!str_detect(img_file_1, "practice_images")) %>%
  # -- remove AC fails -- #
  filter(!pid %in% ac_fail_pids) %>% 
  # -- remove incomplete runs -- #
  filter(!run_id %in% df_incomplete_runs$run_id) %>%
  # -- remove second attempts --#
  filter(run_id %in% df_remove_secondTry_pids$run_id) %>%
  # -- preproc -- #
  select(pid, trial_index, trial_valence,
         img_file_chosen_1, img_file_chosen_2,
         img_file_1, img_file_2, img_file_3) %>% 
  pivot_longer(c(img_file_1, img_file_2, img_file_3), 
               values_to="img_file", names_to="label") %>% 
  mutate(is_chosen=ifelse(img_file == img_file_chosen_1 | 
                            img_file == img_file_chosen_2, 
                          1, 0)) %>% 
  select(-c(img_file_chosen_1, img_file_chosen_2)) %>% 
  arrange(pid, trial_index, img_file)

df_trials_wide <- df_trials %>% 
  arrange(pid, trial_index, desc(is_chosen), img_file) %>% 
  select(-label) %>% 
  group_by(pid, trial_index, trial_valence) %>% 
  mutate(img_num = 1:n()) %>% 
  ungroup %>% 
  pivot_wider(id_cols = c(pid, trial_index, trial_valence), 
              names_from = img_num, values_from=c(img_file, is_chosen)) 

df_trials_chosen <- df_trials_wide %>% 
  select(pid, trial_index, trial_valence, img_file_1, img_file_2) %>% 
  mutate(chosen = 1)
df_trials_unchosen1 <- df_trials_wide %>% 
  select(pid, trial_index, trial_valence, img_file_1, img_file_3) %>% 
  rename(img_file_2 = img_file_3) %>% 
  mutate(chosen = 0)
df_trials_unchosen2 <- df_trials_wide %>% 
  select(pid, trial_index, trial_valence, img_file_2, img_file_3) %>% 
  rename(img_file_1 = img_file_2) %>% 
  rename(img_file_2 = img_file_3) %>% 
  mutate(chosen = 0)
df_trials_weights <- df_trials_chosen %>% 
  bind_rows(df_trials_unchosen1) %>% 
  bind_rows(df_trials_unchosen2) %>% 
  # -- standardize placement of images files in img_file_1 or img_file_2 -- #
  mutate(img1_tmp = map2_chr(img_file_1, img_file_2, ~sort(c(.x, .y))[1])) %>% 
  mutate(img2_tmp = map2_chr(img_file_1, img_file_2, ~sort(c(.x, .y))[2])) %>% 
  mutate(img_file_1 = img1_tmp) %>% 
  mutate(img_file_2 = img2_tmp) %>% 
  select(-img1_tmp, -img2_tmp)
  
  

```

# Create graphs community structure and fit clustering

Create clusters using walktrap algorithm

[A Comparative Analysis of Community Detection Algorithms on Artificial Networks](https://www.nature.com/articles/srep30750.pdf)

Two ways of making graphs: 
  * Only consider when images were chosen together
  * Factor in when images were chosen together and when they were not chosen together
```{r}
# get_graph <- function(df=df_trials_wide){
#    df %>%
#     select(img_file_1, img_file_2) %>%
#     graph_from_data_frame(directed=FALSE)
# }

# # Sum chosen
# get_graph <- function(df){
#   # Takes a dataframe with a single participant and single trial valence
#   dat <- df %>%
#     group_by(img_file_1, img_file_2) %>%
#     summarize(sum_chosen = sum(chosen)) %>%
#     ungroup
#   g <- dat %>%
#     select(img_file_1, img_file_2) %>%
#     graph_from_data_frame(directed=FALSE)
#   E(g)$weight <- dat$sum_chosen
#   return(g)
# }

# Proportion chosen 
get_graph <- function(df){
  # Takes a dataframe with a single participant and single trial valence
  dat <- df %>%
    group_by(img_file_1, img_file_2) %>%
    summarize(pr_chosen = mean(chosen)) %>%
    ungroup
  g <- dat %>%
    select(img_file_1, img_file_2) %>%
    graph_from_data_frame(directed=FALSE)
  E(g)$weight <- dat$pr_chosen
  return(g)
}


# dat <- df_trials_weights %>% 
#   filter(pid == 6591) %>% 
#   group_by(pid, trial_valence, img_file_1, img_file_2) %>% 
#   filter(trial_valence=="negative") %>% 
#   summarize(pr_chosen = mean(chosen)) %>% 
#   ungroup
# g <- dat %>% 
# 
#   select(img_file_1, img_file_2) %>% 
#   graph_from_data_frame(directed=FALSE)
# E(g)$weight <- dat$pr_chosen  
#   
# 
# plot(
#   cluster_walktrap(g),
#   g, 
#   # vertex.size = 10, 
#   vertex.size = strength(g), 
#   vertex.frame.color = NA, 
#   vertex.label.cex = .7,  
#   vertex.label.color = "black",
#   # vertex.label = NA,
#   edge.curved = .2, 
#   edge.width = E(g)$weight,
#   layout = layout.fruchterman.reingold(g)
# )
#   
  
df_graphs <- df_trials_weights %>% 
  group_by(pid, trial_valence) %>% 
  nest() %>%
  mutate(graph = map(data, get_graph)) %>% 
  mutate(cluster = map(graph, cluster_walktrap)) %>% 
  mutate(modularity = map_dbl(cluster, modularity)) %>% 
  mutate(transitivity = map_dbl(graph, transitivity)) %>% 
  # mutate(smallworldness = map_dbl(graph, ~smallworldness(.)["smallworldness"])) %>% # takes a ridiculous amount of time
  mutate(n_clusters = map_dbl(cluster, ~length(unique(.$membership)))) %>% 
  mutate(adjacency_matrix = map(graph, ~get.adjacency(., attr="weight", sparse=FALSE))) %>% 
  mutate(sparsity = map_dbl(adjacency_matrix, ~ mean(. != 0))) %>% 
  ungroup
```

# Combine graphs and survey
```{r}
df_graphs_survey <- df_graphs %>% 
  inner_join(df_survey) 
```


```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

# Sample characteristics

## Number of rows per participant

```{r}
df_trials_weights %>% 
  group_by(pid) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>% 
  kbl %>% 
  kable_styling %>% 
  scroll_box(height="500px", width = "300px")

df_trials_weights %>% pull(pid) %>% unique
df_trials_weights %>% pull(pid) %>% unique %>% length
```

## Response time distribution

```{r}
# participant mean response time
df_task %>% 
  mutate(rt = as.numeric(rt)/1000) %>% 
  filter(rsurveyutils::scale(rt) < 3) %>% # remove outliers if 3 SDs above mean
  group_by(pid) %>% 
  summarize(mean_rt = mean(rt)) %>% 
  ggplot(aes(x = mean_rt)) + 
  geom_histogram()

# trial response time
df_task %>% 
  mutate(rt = as.numeric(rt)/1000) %>% 
  filter(rsurveyutils::scale(rt) < 3) %>% # remove if 3 SDs above mean
  ggplot(aes(x = rt)) + 
  geom_histogram()

```

## Plot total time spent on survey

```{r}
df_task %>% 
  group_by(run_id) %>% 
  filter(time_elapsed == max(time_elapsed)) %>% 
  ungroup %>% 
  mutate(mins_elapsed = as.numeric(time_elapsed)/(1000*60)) %>% 
  ggplot(aes(x = mins_elapsed)) + 
  geom_histogram()

```

## Histogram sparsity of adjacency matrix
```{r}
df_graphs$sparsity %>% hist
```

# Plot all participant networks and clusters and export to PDF

I'm also including their PAQ score and their responses to the attention checks in the within person network PDFs.

```{r eval=FALSE}
clusterPlots_dir <- here(paste0("results/", Sys.Date(), "/clusterPlots"))
dir.create(clusterPlots_dir, recursive=TRUE)
pdf(paste0(clusterPlots_dir, "/pid_valence_clusterPlots.pdf"))
for(i in 1:nrow(df_graphs)){
  plot(
    df_graphs$cluster[[i]],
    df_graphs$graph[[i]],
    # vertex.size = 10,
    vertex.size = strength(df_graphs$graph[[i]]),
    vertex.frame.color = NA,
    vertex.label.cex = .7,
    vertex.label.color = "black",
    # vertex.label = NA,
    edge.curved = .2,
    edge.width = E(df_graphs$graph[[i]])$weight,
    layout = layout.fruchterman.reingold(df_graphs$graph[[i]])
  )
# get free response dimensions of clustering
  freeResp <- df_task %>%
    dplyr::filter(pid == df_graphs$pid[[i]]) %>%
    dplyr::filter(ac_freeResp != "") %>%
    dplyr::filter(trial_valence == df_graphs$trial_valence[[i]]) %>%
    pull(ac_freeResp)
  if(length(freeResp) > 0){
    text(0,-1.4, labels=paste(freeResp, collapse = "\n"))
  }
  # get pid
  text(-1.2,1.4, labels=paste("PID: ", df_graphs$pid[[i]]))
  # get attention check score
  pr_correct <- df_ac_forceChoice %>%
    dplyr::filter(pid == df_graphs$pid[[i]]) %>%
    pull(pr_correct)
  text(-1.2,1.3, labels=paste("AC correct pr:", round(pr_correct, 2)))
  # get PAQ score
  paq_score <- df_survey %>%
    dplyr::mutate(paq = rsurveyutils::scale(paq)) %>%
    dplyr::filter(pid == df_graphs$pid[[i]]) %>%
    pull(paq)
    text(-1.2,seq(1.1, by = -.1, length.out = length(paq_score)),
         labels=paste("PAQ:", round(paq_score, 2)))

}
dev.off()
```

# Plot between participant networks
```{r}
df_graph_full_neg <- df_trials_weights %>% 
  filter(trial_valence == "negative") %>% 
  group_by(img_file_1, img_file_2) %>% 
  summarize(weight = mean(chosen)) %>% 
  ungroup %>% 
  filter(weight > 0)
graph_full_neg <- df_graph_full_neg %>% 
  select(img_file_1, img_file_2) %>% 
  graph_from_data_frame(directed=FALSE)
E(graph_full_neg)$weight <- df_graph_full_neg$weight
# graph_full_neg$weight <- df_graph_full_neg$weight
graph_full_neg %>% 
   plot(
    cluster_walktrap(.),
    .,
    vertex.size = strength(.)/30,
    vertex.frame.color = NA,
    vertex.label.cex = .7,
    vertex.label.color = "black",
    # vertex.label = NA,
    edge.curved = .2,
    edge.width = E(.)$weight,
    layout = layout.fruchterman.reingold(.)
    # layout = layout.kamada.kawai(.)
   )
centralityPlot(graph_full_neg, scale="raw", include = c("Degree", "Betweenness", "Closeness"))
hist(E(graph_full_neg)$weight)
betweenness(graph_full_neg)
tibble(
  betweenness = betweenness(graph_)
)
```

* Why do I need to filter weight > 0 to show betweenness
* Why can't I see strength in centralityplot
* Why are centrality metrics all the same
```{r}
df_graph_full_neutral <- df_trials_weights %>% 
  filter(trial_valence == "neutral") %>% 
  group_by(img_file_1, img_file_2) %>% 
  summarize(weight = mean(chosen)) %>% 
  ungroup %>% 
  filter(weight >0)
graph_full_neutral <- df_graph_full_neutral %>% 
  select(img_file_1, img_file_2) %>% 
  graph_from_data_frame(directed=FALSE)
E(graph_full_neutral)$weight <- df_graph_full_neutral$weight
# graph_full_neutral$weight <- df_graph_full_neutral$weight
graph_full_neutral %>% 
   plot(
    cluster_walktrap(.),
    .,
    vertex.size = strength(.)/30,
    vertex.frame.color = NA,
    vertex.label.cex = .7,
    vertex.label.color = "black",
    # vertex.label = NA,
    edge.curved = .2,
    # edge.width = E(.)$weight,
    edge.width = E(.)$weight,
    layout = layout.fruchterman.reingold(.)
    # layout = layout.kamada.kawai(.)
   )
centralityPlot(graph_full_neutral, include = c("Strength", "Betweenness", "Closeness"))
hist(E(graph_full_neutral)$weight)
betweenness(graph_full_neutral)
```

# Export adjacency matrices of participants
```{r}
adjMatrix_dir <- here(paste0("data/proc/adjacencyMatrices/", Sys.Date(), "/"))
dir.create(adjMatrix_dir, recursive=TRUE)
for(i in 1:nrow(df_graphs)){
  adj_mat <- get.adjacency(df_graphs$graph[[i]], attr="weight", sparse=FALSE)
  # print(dim(adj_mat))
  write.csv(x=adj_mat, file=paste0(adjMatrix_dir, df_graphs$pid[[i]], "_", 
                                   df_graphs$trial_valence[[i]], "_adjMatrix.csv"))
}

```


# Differences by trial valence

Here I'm exploring whether network metrics are different depending on what valence type of block the participant was in

## Modularity metric per trial valence

[Modularity metric](https://en.wikipedia.org/wiki/Modularity_(networks))

```{r}
df_graphs %>% 
  ggplot(aes(y = modularity, x = trial_valence)) + 
  # geom_point(alpha = .3, position=position_jitter(.1)) +
  stat_summary(fun.data = "mean_cl_boot") 

df_graphs %>% 
  lmer(modularity ~ (1|pid), .) %>% 
  summary
df_graphs %>% 
  lmer(modularity ~ trial_valence + (1|pid), .) %>% 
  summary
```


## Mean clusters per trial valence

```{r}
df_graphs %>% 
  ggplot(aes(y = n_clusters, x = trial_valence)) + 
  # geom_point(alpha = .3, position=position_jitter(.1)) + 
  stat_summary(fun.data = "mean_cl_boot") 

df_graphs %>% 
  lmer(n_clusters ~ (1|pid), .) %>% 
  summary
df_graphs %>% 
  lmer(n_clusters ~ trial_valence + (1|pid), .) %>% 
  summary

```

# Relationship between modularity metric and number of clusters metric

```{r}
cor.test(df_graphs$modularity, df_graphs$n_clusters)
```

# Relation of modularity to alexithymia

Here and in the valence analysis, the modularity metric is not behaving as expected. I have not continued with modularity analyses beyond the full scale of alexithymia for this reason.

```{r}
dat <- df_survey %>% 
  select(pid, paq) %>% 
  inner_join(df_graphs)

df_graphs_survey %>% 
  ggplot(aes(x = paq, y = modularity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

# df_graphs_survey %>% 
#   lmer(modularity ~ paq + (1|pid), .) %>% 
#   summary
```

# Relation of n clusters to variables
```{r}
df_graphs_survey %>% 
  ggplot(aes(n_clusters)) +
  geom_histogram()+
  facet_wrap(~trial_valence)
```

## Alexithymia

```{r}
## Full scale
df_graphs_survey %>% 
  ggplot(aes(x = paq, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq, .) %>% 
  summary

## DIF

df_graphs_survey %>% 
  ggplot(aes(x = paq_dif, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

# DDF
df_graphs_survey %>% 
  ggplot(aes(x = paq_ddf, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## EOT
df_graphs_survey %>% 
  ggplot(aes(x = paq_eot, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## PAQ Pos
df_graphs_survey %>% 
  ggplot(aes(x = paq_pos, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_pos, .) %>% 
  summary
  

## PAQ Neg 
df_graphs_survey %>% 
  ggplot(aes(x = paq_neg, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ paq_neg, .) %>% 
  summary
  


```

## ERQ Reappraisal
```{r}
df_graphs_survey %>% 
  ggplot(aes(x = erq_reap_fr, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

df_graphs_survey %>% 
  filter(trial_valence == "negative" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ erq_reap_fr, . ) %>% 
  summary

df_graphs_survey %>% 
  filter(trial_valence == "negative" | trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ erq_reap_fr*trial_valence, . ) %>% 
  summary

```

## ERQ suppression
```{r}
df_graphs_survey %>% 
  ggplot(aes(x = erq_supp_fr, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

df_graphs_survey %>% 
  filter(trial_valence == "negative" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ erq_supp_fr, . ) %>% 
  summary

df_graphs_survey %>% 
  filter(trial_valence == "negative" | trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ erq_supp_fr*trial_valence, . ) %>% 
  summary

```

## PHQ
```{r}
df_graphs_survey %>% 
  ggplot(aes(x = phq, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3, position = position_dodge(.6)) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ phq, . ) %>% 
  summary

df_graphs_survey %>% 
  filter(trial_valence == "negative" | trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ phq*trial_valence, . ) %>% 
  summary

```

## GAD
```{r}

df_graphs_survey %>% 
  ggplot(aes(x = gad, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3, position = position_dodge(.6)) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ gad, . ) %>% 
  summary

df_graphs_survey %>% 
  filter(trial_valence == "negative" | trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ gad*trial_valence, . ) %>% 
  summary

```

## Fatigue
```{r}

df_graphs_survey %>% 
  ggplot(aes(x = fss, y = n_clusters, color = trial_valence)) + 
  geom_point(alpha = .3, position = position_dodge(.6)) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ fss, . ) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive" ) %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ fss, . ) %>% 
  summary

df_graphs_survey %>% 
  filter(trial_valence == "negative" | trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(n_clusters ~ fss*trial_valence, . ) %>% 
  summary

```


# Transitivity
## Alexithymia

```{r}
## Full scale
df_graphs_survey %>% 
  ggplot(aes(x = paq, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq, .) %>% 
  summary

## DIF

df_graphs_survey %>% 
  ggplot(aes(x = paq_dif, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

# DDF
df_graphs_survey %>% 
  ggplot(aes(x = paq_ddf, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## EOT
df_graphs_survey %>% 
  ggplot(aes(x = paq_eot, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## PAQ Pos
df_graphs_survey %>% 
  ggplot(aes(x = paq_pos, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_pos, .) %>% 
  summary
  

## PAQ Neg 
df_graphs_survey %>% 
  ggplot(aes(x = paq_neg, y = transitivity, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_neg, .) %>% 
  summary
  


```

# Smallworldiness
```{r}
## Full scale
df_graphs_survey %>% 
  ggplot(aes(x = paq, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq, .) %>% 
  summary

## DIF

df_graphs_survey %>% 
  ggplot(aes(x = paq_dif, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

# DDF
df_graphs_survey %>% 
  ggplot(aes(x = paq_ddf, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## EOT
df_graphs_survey %>% 
  ggplot(aes(x = paq_eot, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")

## PAQ Pos
df_graphs_survey %>% 
  ggplot(aes(x = paq_pos, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(transitivity ~ paq_pos, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq_pos, .) %>% 
  summary
  

## PAQ Neg 
df_graphs_survey %>% 
  ggplot(aes(x = paq_neg, y = smallworldness, color = trial_valence)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method="lm")
df_graphs_survey %>% 
  filter(trial_valence == "negative") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "neutral") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq_neg, .) %>% 
  summary
df_graphs_survey %>% 
  filter(trial_valence == "positive") %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(smallworldness ~ paq_neg, .) %>% 
  summary
   
  
```


# Session Info

```{r}
sessionInfo()
```
